Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-13 latex_files/applied_network_science_article/article_v0.tex
put pseudocode for the algorithm

@@

>>>>

\subsubsection{Algorithm pseudocode}

\begin{algorithm}[H]
	\caption{Compute the transportation flow matrix $\mathbf{N} = (n_{st})$ knowing the edge-trip incidence matrix $\bm{\chi} = (\chi_{ij}^{st})$, the set of transfer edges $\mathcal{T}$, the embarking flow $\mathbf{a}$, the disambarking flow $\mathbf{b}$, the index of an isolated source node $\tilde{s}$, and the minimum proportion of passengers entering/leaving the network $\theta$.}
	\label{algo1}
	\begin{algorithmic}[1]
		\State $g_{st} \leftarrow I(\chi_{\bullet \bullet}^{st} > 0) / \sum_{s't'}I(\chi_{\bullet \bullet}^{s't'} > 0), \; \forall s,t$ \Comment{{\footnotesize Initialize the prior distribution}}

		\State $\alpha_s \leftarrow a_s / a_\bullet, \; \forall s,t$ \Comment{{\footnotesize Initialize the network ingoing distribution}}

		\State $\beta_t \leftarrow b_t / b_\bullet, \; \forall t$ \Comment{{\footnotesize Initialize the network outgoing distribution}}

		\State $\epsilon \leftarrow 10^{-40}$ \Comment{{\footnotesize Fix a small quantity}}

		\While{$\mathbf{N} = (n_{st})$ has not converge} \Comment{{\footnotesize Main loop}}

		\State $\psi_t \leftarrow 1, \; \forall t$

		\While{$\bm{\psi} = (\psi_t)$ has not converge} \Comment{{\footnotesize Iterative fitting loop}}

		\State $\phi_s \leftarrow \alpha_s / (\sum_t \psi_t g_{st} + \epsilon), \; \forall s$
		\State $\psi_t \leftarrow \beta_t / (\sum_s \phi_s g_{st} + \epsilon), \; \forall t$

		\EndWhile

		\State $n_{st} \leftarrow \frac{a_{\tilde{s}}}{\alpha_{\tilde{s}}} \phi_s \psi_t g_{st}, \; \forall s,t$ \Comment{{\footnotesize Compute the transportation flow}}

		\State $z_{ij} \leftarrow I((i,j) \in \mathcal{T})\sum_{st} \chi_{ij}^{st} n_{st}, \; \forall i,j$

		\State $\alpha_s \leftarrow \frac{\min(\theta a_s, a_s - z_{\bullet s})}{\sum_{s'} \min(\theta a_{s'}, a_{s'} - z_{\bullet {s'}})}, \; \forall s$ \Comment{{\footnotesize Update the network ingoing distribution}}

		\State $\beta_t \leftarrow \frac{\min(\theta b_t, b_t - z_{t \bullet})}{\sum_{t'} \min(\theta b_{t'}, b_{t'} - z_{{t'} \bullet})}, \; \forall t$ \Comment{{\footnotesize Update the network outgoing distribution}}

		\State $r_{ij} \leftarrow \max \left(1, \frac{z_{i \bullet}}{(1 - \theta)b_i}, \frac{z_{\bullet j}}{(1 - \theta)a_j} \right), \; \forall i,j$

		\State $\bar{r}_{st} \leftarrow \max_{ij} \chi_{ij}^{st} r_{ij}, \; \forall s,t$

		\State $\widetilde{g}_{st} \leftarrow \frac{\left( \frac{n_{st}}{\phi_s \psi_t \bar{r}_{st} + \epsilon} \right)}{\sum_{s',t'} \left( \frac{n_{s't'}}{\phi_{s'} \psi_{t'}\bar{r}_{s't'} + \epsilon} \right) + \epsilon}, \; \forall s,t$ \Comment{{\footnotesize Update the prior distribution}}

		\EndWhile
		\State \Return $\mathbf{N} = (n_{st})$
	\end{algorithmic}
\end{algorithm}

@@

***  @G, ici davantage de développements sur l'approche Markovienne, ainsi que le joli schéma ?  ***

\

*** @G, @R, ici la (les) figure de l'exemple  ``starting from Maladière, Riant-Cour, Dapples"... ? ***
